### 2023-04-17 chapter1/chapter1.tex
Correct use of homology to orthology for consistency
Added reference for Felsenstein's pruning algorithm

\begin{figure}[h!]
\includegraphics[width=\textwidth]{graphical_overview/out/graphical_overview.png}
\centering
\caption{\textbf{Overview of homology inference pipeline.}
\textbf{(A-C)} The large, open circles represent the annotated genomes, and the small, filled circles represent the protein sequences associated with each annotation. Sequences that share homology are colored with shades of the same hue. \textbf{(D-F)} The small, filled circles and lines represent the same sequences and best hits from the previous steps.}
\label{fig:graphical_overview}
\end{figure}

@@

All HMM algorithms were implemented with custom code which is available as the package Homomorph on PyPI. The insertion phylo-HMM was trained on 47,387 manually labeled columns in 14 alignments, and the missing data phylo-HMM was trained on 67,001 manually labeled positions in 23 sequences in 11 unique alignments (Fig.~\ref{sfig:insertion_training}, Fig.~\ref{sfig:missing_training}). Because maximum-likelihood estimation of the model parameters yielded posterior decoding curves which toggled between hidden states too rapidly, the models were instead trained discriminatively~\cite{Krogh1999}. The difference, briefly, is maximum-likelihood estimation finds the parameters that best reproduce the observed distributions whereas discriminative training finds the parameters that minimize prediction error. Discriminatively trained models typically perform better in practice since real-world data are rarely fully described by the distribution specified by the model.

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{graphical_overview/out/graphical_overview.png}
\centering
\caption{\textbf{Overview of orthology inference pipeline.}
\textbf{(A-C)} The large, open circles represent the annotated genomes, and the small, filled circles represent the protein sequences associated with each annotation. Sequences that share homology are colored with shades of the same hue. \textbf{(D-F)} The small, filled circles and lines represent the same sequences and best hits from the previous steps.}
\label{fig:graphical_overview}
\end{figure}

@@

The likelihoods of phylogenetic trees were efficiently calculated with Felsenstein's pruning algorithm, and all HMM algorithms were implemented with custom code which is available as the package Homomorph on PyPI~\cite{Felsenstein1981}. The insertion phylo-HMM was trained on 47,387 manually labeled columns in 14 alignments, and the missing data phylo-HMM was trained on 67,001 manually labeled positions in 23 sequences in 11 unique alignments (Fig.~\ref{sfig:insertion_training}, Fig.~\ref{sfig:missing_training}). Because maximum-likelihood estimation of the model parameters yielded posterior decoding curves which toggled between hidden states too rapidly, the models were instead trained discriminatively~\cite{Krogh1999}. The difference, briefly, is maximum-likelihood estimation finds the parameters that best reproduce the observed distributions whereas discriminative training finds the parameters that minimize prediction error. Discriminatively trained models typically perform better in practice since real-world data are rarely fully described by the distribution specified by the model.
